A Formal Verification Framework for Smart Contracts Based on Symbolic Execution

### 2024-01-17 papers/static-checker/ecoop2024/ecoop2024.tex
aution contract specification

Our starting point is the design of a domain-specific language for
specifying smart contract properties.
\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification (excerpt)},label={lst:auction-fragment}]
mcontract auction = spec 
  storage := Pair (auction_open: bool) 
                  Pair (highest_bidder: address)
                       (contract_owner: address))
  entrypoint %bid
    code := {...}
    parameter := Unit 
    pre-condition := auction_open 
       && Amount > pre_Balance 
       && get_contract (unit, highest_bidder) = 
          Some (c: contract unit)
    post-condition := auction_open
       && post_highest_bidder = Sender 
       && post_contract_owner = contract_owner 
       && post_Balance = Amount 
       && transfer_token (Unit, Old_Balance, c) ;
\end{lstlisting}
As an example, Listing~\ref{lst:auction-fragment} contains an excerpt
of the specification of an auction contract. The \texttt{storage}
phrase describes the internal state (storage) of the contract
consisting of three values named \lstinline|auction_open|,
\lstinline|highest_bidder|, and \lstinline|contract_owner|.
The contract has several entrypoints that may be invoked individually.

>>>>

Our starting point is the design of a domain-specific language for
specifying smart contract properties.
\begin{lstlisting}[float=tp,captionpos=b,caption={Auction contract specification (excerpt)},label={lst:auction-fragment}]
mcontract auction = spec 
  storage := Pair (auction_open: bool) 
                  Pair (highest_bidder: address)
                       (contract_owner: address))
  entrypoint %bid
    code := {...}
    parameter := Unit 
    pre-condition := auction_open = true
       && Amount > pre_Balance 
       && get_contract (unit, highest_bidder) = 
          Some (c: contract unit)
    post-condition := auction_open
       && post_highest_bidder = Sender 
       && post_contract_owner = contract_owner 
       && post_Balance = Amount 
       && transfer_token (Unit, pre_Balance, c) ;
\end{lstlisting}
As an example, Listing~\ref{lst:auction-fragment} contains an excerpt
of the specification of an auction contract. The \texttt{storage}
phrase describes the internal state (storage) of the contract
consisting of three values named \lstinline|auction_open|,
\lstinline|highest_bidder|, and \lstinline|contract_owner|.
The contract has several entrypoints that may be invoked individually.
